### 2016-11-05 taylor_series.tex
more shit

where $\Delta E_k$ is the change in the total error of the network when exactly one neuron ($k$) is turned off.

>>>>

where $\Delta E_k$ is the change in the total error of the network when exactly one neuron ($k$) is turned off. Most of the terms in this equation are fairly easy to compute, as we have $O_k$ already from the activations of the hidden units and we already compute $\pdv{E}{O}|_{O_k}$ for each training instance during backpropagation. The $\small{\pdv[2]{E}{O}|_{O_k}}$ terms are a little more difficult to compute. This is derived in the appendix and summarized in the sections below.
